\subsection{Methodology}
This reproduction did \emph{not} use the authors' original code. Instead, it used an original implementation located under \texttt{src/Kun/scripts}, with one script per reproduced result: \texttt{make\_figure2.py}, \texttt{make\_figure3.py}, \texttt{make\_figure5.py}, and \texttt{make\_table1.py}. The implementation follows the procedure described in the paper and relies on public pretrained checkpoints loaded through \texttt{timm}, \texttt{open\_clip\_torch}, and Hugging Face \texttt{transformers}. Dataset loading is done through \texttt{torchvision} where possible otherwise is done through direct download from the dataset official website.

\subsubsection{Datasets}

\paragraph{Figures 2, 3, and 5.}
all runs for Figures~2, 3, and 5 uses \texttt{Caltech101 via torchvision} as the image source.


\paragraph{Table 1 datasets.}
We use a subset of the following datasets:
\begin{itemize}
    \item \texttt{cifar10, 10 classes}
    \item \texttt{cifar100, 100 classes}
    \item \texttt{caltech101, 101 classes}
    \item \texttt{dtd, 47 classes}
    \item \texttt{aircraft, 100 classes} 
    \item \texttt{flowers102, 102 classes}
    \item \texttt{food101, 101 classes}
\end{itemize}
For each datasets we sample 500 training and 200 test images balanced across labels.

\subsubsection{Hyperparameters}

The most important hyperparameter across these experiments is the minimum norm value a patch feature vector must have in order to be considered as an outlier patch. In the paper this cutoff value is set heuristically to 150. 
\begin{itemize}
    \item For the 2 experiments in figure5 we use the same cutoff value.
    \item For the Table1 experiments, outliers are defined using a soft cutoff equal to the 99th percentile of training-set patch norms, so that approximately 1\% of patches are labeled as outliers. In addition, if a given image contains no outlier patch under this rule, we fall back to selecting the highest-norm patch from that image as its outlier token.
\end{itemize}

\begin{table}[h]
    \centering
    \caption{Hyperparameters for the Figure~5b linear probes.}
    \label{tab:figure5b-hparams}
    \begin{tabular}{ll}
        \toprule
        Hyperparameter & Value \\
        \midrule
        Train fraction & 0.75 \\
        Max epochs & 80 \\
        Batch size & 512 \\
        Learning rate & 0.001 \\
        Optimizer & AdamW \\
        Weight decay & $10^{-4}$ \\
        Early stopping patience & 3 \\
        Position probe loss & Cross-entropy \\
        Reconstruction probe loss & MSE \\
        Feature dimension & 1536 \\
        Number of positions & 256 \\
        Pixel target dimension & 588 \\
        \bottomrule
    \end{tabular}
\end{table}

\subsubsection{Experimental setup and code}

\paragraph{Figure 2 attention maps.}
\texttt{make\_figure2.py} loads the 6 model families indicated by the paper and outputs the attention map, extracted from the last self-attention layer, of 4 random images.

\paragraph{Figure 3 norm analysis.}
\texttt{make\_figure3.py} compares the local features norms distribution for \texttt{DINO ViT-B/16} and \texttt{DINOv2 ViT-g/14} both on a single image and on a batch of 1000 images.

\paragraph{Figure 5 local information probing.}
\texttt{make\_figure5.py} uses\texttt{DINOv2 ViT-g/14} only and compares the cosine similarity of outlier/normal patches to its neighbor patches across 100 images. 
In addition it performs linear probing for local information by training:
\begin{itemize}
    \item a linear classifier for patch-position prediction, and
    \item a linear regressor for patch-pixel reconstruction.
\end{itemize}.
Linear probing is done with 500 images. 

\paragraph{Table 1 image classification probes.}
\texttt{make\_table1.py} uses \texttt{DINOv2 ViT-g/14} as a frozen feature extractor:
For each image in the dataset, the script extracts three candidate representations: the \texttt{[CLS]} token, one normal patch token, and one outlier patch token. It then trains three separate multinomial logistic regression classifiers, one per representation type.

\paragraph{Parameter counts.}
The scripts do not record parameter counts. Insert the values here if they are needed in the final report:
\begin{itemize}
    \item DeiT-III-B: \texttt{[INSERT PARAMETER COUNT]}
    \item DeiT-III-L: \texttt{[INSERT PARAMETER COUNT]}
    \item OpenCLIP ViT-B-16: \texttt{[INSERT PARAMETER COUNT]}
    \item OpenCLIP ViT-L-14: \texttt{[INSERT PARAMETER COUNT]}
    \item DINO ViT-B/16: \texttt{[INSERT PARAMETER COUNT]}
    \item DINOv2 ViT-B/14: \texttt{[INSERT PARAMETER COUNT]}
    \item DINOv2 ViT-L/14: \texttt{[INSERT PARAMETER COUNT]}
    \item DINOv2 ViT-g/14: \texttt{[INSERT PARAMETER COUNT]}
\end{itemize}

\subsubsection{Computational requirements}
The experiments executed locally on an Apple M4 Pro machine with 24\,GB unified memory. The mps backend is used whenever is possible; when some torch implementation are known to be unstable we fall back to cpu. 

The following runtime and compute values should therefore be inserted from recorded experiment logs rather than inferred here:
\begin{itemize}
    \item \texttt{[INSERT AVERAGE RUNTIME FOR FIGURE 2 IN CPU MODE]}
    \item \texttt{[INSERT AVERAGE RUNTIME FOR FIGURE 3 IN CPU MODE]}
    \item \texttt{[INSERT AVERAGE RUNTIME FOR FIGURE 5a IN CPU MODE]}
    \item \texttt{[INSERT AVERAGE RUNTIME FOR FIGURE 5b IN CPU MODE]}
    \item \texttt{[INSERT AVERAGE RUNTIME FOR TABLE 1 PER DATASET]}
    \item \texttt{[INSERT TOTAL WALL-CLOCK TIME / CPU-HOURS FOR THE REPORTED RUNS]}
\end{itemize}

Qualitatively, the most expensive operations in the scripts are repeated forward passes through DINOv2, especially in exact mode (\texttt{facebook/dinov2-giant}) and on larger datasets. Table~1 and Figure~5b are the most computationally demanding scripts because they combine feature extraction with downstream probe fitting.
