\subsection{Results}
Our results support the paper's central claim: register tokens consistently improve object discovery,
reduce high-norm outliers, and produce cleaner attention patterns across all three model families and
datasets. Absolute CorLoc numbers are systematically 15--20\% below the paper's (see Section~\ref{sec:LOST_gram_matrix}).
\subsubsection{Results reproducing original paper}
\subsubsubsection{\textbf{Object discovery: LOST quantitative evaluation.}}
This result supports the claim that registers improve unsupervised object discovery. Table~\ref{tab:object_discovery} reports our full results alongside the paper's reference numbers. The register improvement is confirmed in the correct direction for almost all six model/dataset combinations

\subsubsubsection{\textbf{Qualitative attention maps.}}
The qualitative attention maps (Figure~\ref{fig:qualitative_attention}) show that CLS attends broadly to the subject, while each register token produces a distinct spatial pattern. The four registers show complementary attention regions, suggesting specialisation.

\subsubsubsection{\textbf{LOST intermediate maps.}} 
Figure~\ref{fig:lost_intermediate_steps} shows that for DINOv2 and DeiT-III, adding registers produces visibly cleaner dot-product and seed expansion maps — the noisy background activations present without registers are reduced. For OpenCLIP, the improvement is less striking, consistent with the paper's finding that OpenCLIP values already suppress outliers even without registers.

Figure~\ref{fig:seed_expansion_openclip} confirms this: the values column (right) is clean in both the no-reg and with-reg rows, which is surprising given the existence of high-norm patches in the output of OpenCLIP without registers (as shown in Figure~\ref{fig:token_norms_openclip}).

\subsubsubsection{\textbf{Norm distributions.}} 
Figure~\ref{fig:token_norms_dinov2} reproduces the paper's key qualitative finding: without registers, patch tokens have a bimodal norm distribution with a high-norm tail alongside normal patches. With 4 registers, this tail disappears — patch norms become uniform — and the register tokens themselves sit at distinct, elevated norm levels. This directly supports the claim that registers absorb the high-norm outlier content.

\subsubsubsection{\textbf{Information held by tokens.}}
Table~\ref{tab:outlier_token_probes} shows linear probe performance on the FGVC-Aircraft dataset of models with and without registers, when using different tokens as representations. Results confirm the paper's core findings that  outlier patches (no-reg) and register tokens (with-reg) hold significantly more global information than normal patches.
Table~\ref{tab:local_information_probes} shows that normal patches hold more local information than outlier patches, and that adding registers does not reduce significantly the local information held by normal patches.

\subsubsubsection{\textbf{Positional focus.}}
Figure~\ref{fig:positional_focus} clearly reproduces the paper's finding: CLS and all four registers exhibit broad, diffuse, centred attention patterns (global focus), while the centre patch token attends sharply and locally to its immediate neighbourhood. This supports the claim that registers take on a global information-gathering role, freeing patch tokens to maintain local spatial representations.