\documentclass[10pt]{article} % For LaTeX2e

% This template and styling file have been adapted from the ML Reproducibility Challenge 2020 and TMLR templates, to ease the submission.

% If you want to show the general instructions, use the following command:
% \usepackage[instructions]{atml}
% For the final version, use this one:
\usepackage{atml}

% If you want to submit this work to tmlr, use the "tmlr" package rather than the "atml" one. Note: double-check the files needed in TMLR's submission instructions. 
% \usepackage{tmlr}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{tmlr}
% To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
%\usepackage[preprint]{tmlr}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage{fontawesome5} 
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{tablefootnote}
\usepackage{float}
\usepackage{multirow}
\usepackage{caption}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1.5ex plus 0.3ex minus 0.2ex}{0pt}
\titlespacing*{\subsection}{0pt}{0.8ex plus 0.2ex}{0pt}
\titlespacing*{\subsubsection}{0pt}{0.5ex plus 0.2ex}{0pt}

\title{ATML Report}

\author{%
  \name Raffaele Perri \email raffaele.perri@usi.ch
  \AND
  \name Paolo Deidda \email paolo.deidda@usi.ch
  \AND
  \name Kun Zhan \email zhank@usi.ch
}

\def\groupid{---}
\def\projectid{ViT Registers}

\begin{document}

\maketitle

\faGithub\ \href{https://github.com/USI-Projects-Collection/Adv_ML}{\texttt{github.com/USI-Projects-Collection/Adv\_ML}}
\vspace{0.5cm}

\begin{abstract}
 This reproducibility report investigates the central claims made in the paper "Vision Transformers Need Registers" \citep{darcet2024vision}. The original work suggests that Vision Transformers (ViTs) generate high-norm outlier tokens in low-information background areas, which are repurposed for global internal computations, leading to corrupted local feature maps. The proposed mechanism to resolve this is the addition of "register tokens", extra learnable tokens appended to the input sequence. Our experiments focus on verifying the emergence and content of these artifacts, the impact of register tokens on linear evaluation tasks and their ablation, and the reproduction of feature quality and object discovery improvements using the LOST algorithm. Overall, our findings robustly support the original claims across different model families and datasets: register tokens successfully absorb outlier token content, improve dense-prediction tasks, and do not degrade global linear performance. We also identify and document limitations related to test-time register proxies and undocumented implementation details.
\end{abstract}

% \newpage
%%%%
\setcounter{tocdepth}{2}
{\setlength{\parskip}{0pt}\linespread{0.9}\selectfont
\tableofcontents
\par}

\newpage
%%%%

\section{Introduction}
Vision Transformers (ViTs) have become standard architectures for computer vision tasks, particularly due to their compelling self-supervised representations. However, they are known to exhibit visual artifacts in the form of high-norm tokens scattered throughout low-informative background areas of the image. The paper "Vision Transformers Need Registers" \citep{darcet2024vision} characterizes these outlier tokens as a product of the attention mechanism repurposing uninformative patches to aggregate and store global image information, which inevitably harms local representations used in dense prediction tasks. 

To address this, the authors introduce the concept of "register tokens", supplementary learnable parameters inserted into the input sequence, serving as a dedicated workspace for global information processing. In this report, we attempt to independently reproduce the core claims of the paper. We start by confirming the underlying phenomena; the emergence of outlier tokens in standard ViT feature maps and their informational content. We then evaluate the effectiveness of register tokens on linear evaluation protocols and study the effect of varying the number of registers. Finally, we reproduce experiments showing that such tokens enhance local feature quality and substantially improve unsupervised object discovery.


\label{sec:claims}
% \newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{inputs/K/K_main.tex}
% \newpage

\input{inputs/P/P_main.tex}
% \newpage

\input{inputs/R/R_main.tex}
% \newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Conclusion}
In this report, we successfully validated the key findings of \citet{darcet2024vision}. First, we corroborated the appearance of high-norm outliers in ViTs, which absorb global information from low-informative patches. Second, we proved that adding register tokens maintains or slightly improves linear evaluation accuracy, whilst significantly assisting dense-prediction tasks. Third, we verified that registers actively store outlier content, maintaining clean local feature quality and enhancing object discovery algorithms like LOST. 

Nevertheless, our study was limited by the unavailability of pre-trained weights for DeiT-III and OpenCLIP variants equipped with native training registers, forcing us to incorporate test-time approximations or inject untrained tokens that complicated exact numerical replications. Furthermore, undocumented implementations, such as the missing per-row mean-centering in the LOST algorithm, created small margins of divergence in downstream accuracy scores. 

Future work could address these limitations by fully re-evaluating the object discovery and localization pipelines on models pre-trained natively with registers from scratch. Investigating the point of collapse (e.g., at $N=16$) observed in our test-time register independent ablation could also provide deeper insights into the capacity bound and behavior of downstream transformer blocks when processing too many simultaneous global broadcast tokens.

\section*{Member contributions}
K.Z. was responsible for reproducing the results of Section 2. \\
P.D. was responsible for reproducing the results of Section 3. \\
R.P. was responsible for reproducing the results of Section 4. \\
This division of work is reflected both in the structure of the repository's \texttt{src/} folder and in the drafting of this report.

\section*{Usage of AI}
AI tools were used for research purposes, coding assistance, and rephrasing of some part of the report for better readability.

%%%%
\newpage
\bibliography{bibliography}
\bibliographystyle{tmlr}

\input{appendix.tex}

\end{document}
