\subsection{Discussion}

Across Table~2a, Table~2b, and Figure~8 our results qualitatively support the central claim of \citet{darcet2024vision} -- that giving a Vision Transformer dedicated register tokens does not degrade downstream performance, and in fact slightly improves all three probes for DINOv2-L/14 (the cleanest comparison, since both checkpoints are released by the authors). For OpenCLIP, since no trained-register checkpoint exists publicly, we rely on the test-time register variant of \citet{jiang2025vision}; on classification this is statistically indistinguishable from the baseline ($-0.67$~pt zero-shot, $0$~pt linear probe), and dense prediction improves marginally, consistent with that paper's claims. The DeiT-III row is an honest negative control: registers bolted on at inference to a model that never saw them during training produce a small Top-1 regression ($-0.67$~pt) but, perhaps surprisingly, still improve patch-level metrics. The overall picture is that the register mechanism is robust enough that even crude approximations do not damage the network's downstream usefulness in a substantial way.

For our additional results on the test-time register method we draw a more nuanced conclusion. Our independent re-implementation reproduces the qualitative behaviour reported in \citet{jiang2025vision}: a single test-time register absorbs the high-norm outlier, the attention map cleans up, and Top-1 jumps to the same plateau reached by trained registers. However when we push the method to many test-time registers (the analogue of the Figure~8 sweep), a clear failure mode appears that the original paper does not test for: Top-1 holds flat from $N=1$ to $N=8$ and then collapses by 3~points at $N=16$. To disentangle the cause we designed a controlled variant in which each of the $N$ registers receives a \emph{distinct} top-$k$ outlier value rather than $N$ identical copies of the top-1. The collapse persists. This rules out duplicated-broadcast as the cause and points instead at a downstream effect in the layers (18--23) that come after the neuron-editing point, which were never trained on so many strongly active broadcast tokens. Within our compute budget this leaves a clean, falsifiable finding: the Jiang method is correctly scoped at $N=1$ and degrades for $N\!\gg\!1$ for reasons that do not lie in the writing policy.

Finally, on the magnitude of the effect: the absolute downstream gains from registers are small ($\sim$+0.7~pt Top-1 on DINOv2 in the original paper, similar in our subset numbers). The principal value of registers is therefore not raw accuracy but interpretability -- the attention maps go from unusable to clean -- and unsupervised tasks that depend on those maps. Our reproduction confirms both: small but consistent quantitative gains, and dramatic qualitative gains visible in Figures~\ref{fig:f8-top-ours},~\ref{fig:f8-top-jiang}, and~\ref{fig:f8-top-jiang-indep}.

\subsubsection{What was easy}

The DINOv2 portion of Table~2a was straightforward because both the baseline and the 4-register checkpoint are released directly by \citet{darcet2024vision} via \texttt{timm}, so the comparison is a clean apples-to-apples evaluation with no architectural ambiguity. Re-implementing the three linear probes (classification, segmentation, depth) was also unproblematic: each is a single \texttt{Conv2d 1x1} or scikit-learn logistic regression on top of frozen features, well-suited to a CPU/MPS-only budget. Identifying the \citet{jiang2025vision} register neurons from scratch was easier than expected: Algorithm~1 of that paper is short and unambiguous, and the fact that five of the top-10 neurons we found on the \texttt{timm} GELU port matched the indices the authors published for the Meta-DINOv2 SwiGLU port gave us immediate confidence that our re-implementation was correct.

\subsubsection{What was difficult}

The hardest part was building credible with-register baselines for OpenCLIP and DeiT-III. \citet{darcet2024vision} report trained-register results for both, but neither checkpoint has been released publicly: this forced us to substitute the OpenCLIP trained variant with the test-time register checkpoint of \citet{jiang2025vision} and to build a DeiT-III ``with registers'' purely by injecting untrained parameter tokens at inference. Both substitutions are documented limitations of the reproduction.

A second difficulty was establishing what ``register'' visualisation in the original Figure~8 is actually plotting. We render the last-layer \texttt{[CLS]}$\to$\texttt{patch} attention map averaged over heads, which is the most natural choice given the paper's wording. Even so, our maps disagree with the paper at $N=0$: \citet{darcet2024vision} show several distinct outlier spots, we show one strong outlier. After exhaustive diagnostics (verifying that the model weights are bit-identical, that pre-processing is correct, and that the patch norms do contain several mid-magnitude outliers) we believe the discrepancy reflects a visualisation choice (their colormap appears to be clipped or log-scaled to make sub-dominant outliers visible) rather than a model-level difference. This is documented in the report so the comparison can be interpreted correctly.

Finally, our \emph{independent} variant of the Jiang method had a non-obvious implementation bug that we caught only after careful diagnostic measurements: zeroing only the top-$N$ outlier positions per neuron (rather than all 1369 patch positions, as Jiang does) leaves residual outliers that re-pollute the attention map. Once corrected, the variant gives clean attention maps but does not, as we initially hypothesised, fix the collapse at $N=16$. This null result is itself informative and is reported as such.

\subsubsection{Communication with original authors}

We did not contact either set of authors. The questions we needed answered were not resolved by the papers alone: the exact visualisation choice for Figure~8, the public availability of trained-register OpenCLIP and DeiT-III checkpoints, and the choice of $N=1$ in \citet{jiang2025vision}'s primary experiments. The first and last are inferable from the papers' code and appendices and we resolved them ourselves; the second is a question that has a clear no answer.
