\subsection{Methodology}
We re-implemented the experiments of Section~3.2 of \citet{darcet2024vision} from scratch in PyTorch, using publicly available pretrained checkpoints from \texttt{timm} \citep{rw2019timm}, \texttt{open\_clip} \citep{ilharco_gabriel_2021_5143773}, and Hugging Face. We did not run the authors' code: the paper does not ship a public training script, and we needed full control over the evaluation pipeline to fit the small-scale compute budget. We additionally implemented from scratch the test-time register method of \citet{jiang2025vision}, since their reference repository targets Meta's native DINOv2 (SwiGLU MLP), while our pipeline uses the \texttt{timm} port (GELU MLP). All code is in \texttt{Adv\_ML/src/Poli/}.

\subsubsection{Model descriptions}
We compare three pretrained Vision Transformer backbones, each in a \emph{no-register} and a \emph{with-register} variant, plus a re-implementation of test-time registers on DINOv2:
\begin{itemize}
    \item \textbf{DINOv2 ViT-L/14} (304M params), pretrained self-supervised on LVD-142M: baseline \texttt{vit\_large\_patch14\_dinov2.lvd142m}, with-register variant \texttt{vit\_large\_patch14\_reg4\_dinov2.lvd142m} (the official 4-register checkpoint from \citet{darcet2024vision}).
    \item \textbf{OpenCLIP ViT-B/16} (86M vision params), pretrained on LAION-2B: baseline \texttt{ViT-B-16 / laion2b\_s34b\_b88k}; with-register variant is the test-time register checkpoint \texttt{amildravid4292/clip-vitb16-test-time-registers} from \citet{jiang2025vision}, as no trained-register OpenCLIP checkpoint exists publicly.
    \item \textbf{DeiT-III ViT-B/16} (86M params), pretrained supervised on ImageNet-22k and fine-tuned on ImageNet-1k: baseline \texttt{deit3\_base\_patch16\_224.fb\_in22k\_ft\_in1k}; with-register variant constructed by injecting 4 zero-initialized register-token \texttt{nn.Parameter}s into the baseline at inference (no retraining is available publicly).
    \item \textbf{DINOv2 +tt-reg} (ours): a re-implementation of \citet{jiang2025vision} Algorithm~1 + Section~4 on top of the \texttt{timm} DINOv2 baseline. The 50 ``register neurons'' are recomputed on our subset; at inference we append $N$ extra register tokens to the sequence and install forward hooks on \texttt{block.mlp.act} for the layers containing the identified neurons.
\end{itemize}
All checkpoints are loaded \emph{frozen}; the only trainable parameters are the linear heads of each downstream probe.

\subsubsection{Datasets}
We use stratified subsets of three datasets, all evaluated on a fixed train/val split (no separate test set, see below):
\begin{itemize}
    \item \textbf{ImageNet-1k} \citep{deng2009imagenet}: 50 randomly chosen classes (seed 42), 10 images per class drawn from the official validation split via Hugging Face \texttt{ILSVRC/imagenet-1k}, then split 7:3 into 350 train + 150 val images. Used for linear-probe Top-1 classification and zero-shot CLIP evaluation.
    \item \textbf{ADE20k} \citep{zhou2017scene}: 500 images sampled stratified from the official validation split (150 semantic classes plus background, ignore-index 0). Split 7:3 into 350 train + 150 val. Used for linear segmentation mIoU.
    \item \textbf{NYU Depth v2} \citep{silberman2012indoor}: 500 RGB+depth pairs from the official Kinect-acquired validation set, split 7:3 into 350 train + 150 val. Used for linear depth RMSE in metres.
\end{itemize}
Images are resized to 518$\times$518 for DINOv2 (its native pretraining resolution) and 224$\times$224 for OpenCLIP/DeiT-III, normalised with ImageNet statistics. For segmentation and depth, the corresponding ground-truth masks are bilinearly resized to the same resolution.
We use only a train/val split (no separate test) because (i) the linear heads have a single regularisation hyperparameter left at default and we do no iterative hyperparameter tuning, so there is no validation-set leakage to control for, and (ii) splitting our 500 images three ways would leave each subset too small for reliable estimates. We declare upfront that absolute numbers will not match those reported on the full datasets; what we compare is the \emph{relative} effect of adding registers.

\subsubsection{Hyperparameters}
The linear-probe head is \texttt{sklearn.LogisticRegression(max\_iter=1000)} fit on frozen \texttt{[CLS]} features; no other hyperparameter tuning. The segmentation head is a $1\!\times\!1$ \texttt{Conv2d}($C \to 151$), trained with cross-entropy (ignore-index 0) and AdamW (lr $10^{-3}$, weight-decay $10^{-2}$) for 30 epochs on batch-size~4. The depth head is the same $1\!\times\!1$ \texttt{Conv2d}($C \to 1$) trained on log-depth with MSE, identical optimiser and schedule, with output clamped to the dataset depth range before \texttt{exp}. For Figure~8 we sweep $N \in \{0, 1, 2, 4, 8, 16\}$ registers. For the test-time register experiments (re-implementation of \citet{jiang2025vision}) we use the hyperparameters from their \texttt{configs/dinov2\_large.yaml}: \texttt{top\_k = 50}, \texttt{register\_norm\_threshold = 150}, \texttt{highest\_layer = 17}, \texttt{detect\_outliers\_layer = -2}, and we identify the register neurons on 100 ImageNet training images.

\subsubsection{Experimental setup and code}
For Table~2a we run the three probes on each of the six $\{$backbone$\}\times\{$no-reg, with-reg$\}$ combinations. For Table~2b we run zero-shot ImageNet classification on OpenCLIP using the standard 11-prompt template ensemble averaged in CLIP's joint embedding space. For Figure~8 (top) we render the last-layer \texttt{[CLS]}$\to$\texttt{patch} attention map of DINOv2 on the same image used by \citet{darcet2024vision}, with the model's \texttt{fused\_attn} disabled so that explicit softmax probabilities can be captured via a forward hook. For Figure~8 (bottom) we run the same three probes for each $N$. Performance metrics are Top-1 accuracy for classification, mean Intersection-over-Union for segmentation, and Root-Mean-Squared-Error in metres for depth. All code, evaluation scripts, and JSON result dumps live in \texttt{Adv\_ML/src/Poli/}.

\subsubsection{Computational requirements}
All experiments ran on a single Apple M-series chip via the PyTorch MPS backend; no dedicated GPU was used. A single DINOv2 linear probe on the full subset (350 train + 150 val) takes $\sim$3 minutes; segmentation takes $\sim$9 minutes; depth $\sim$5 minutes. Each Figure~8 sweep over $N \in \{0,1,2,4,8,16\}$ on DINOv2 therefore amounts to $\sim$1.5--2.5 hours of wall-clock time. The full set of experiments in this report (Table~2a, Table~2b, Figure~8 bottom for three sweeps: truncate/cycle, test-time registers, independent test-time registers, plus three Figure~8 top renderings) ran in approximately 10 hours of total compute on the local machine.
