\subsection{Results}
\label{sec:results-P}

\subsubsection{Results reproducing original paper}

\subsubsubsection{Table 2 -- Linear and zero-shot evaluation with frozen features}

Table~\ref{tab:t2ab} reports the three linear probes (Top-1 / mIoU / RMSE) for each backbone with and without registers (left), and the OpenCLIP zero-shot Top-1 (right).

\begin{minipage}{\linewidth}
    \centering
    \resizebox{\linewidth}{!}{%
    \begin{tabular}{@{}c@{\hspace{1.5em}}c@{}}
        \begin{tabular}[b]{lccc}
        \toprule
        & \textbf{ImageNet} & \textbf{ADE20k} & \textbf{NYUd} \\
        \textbf{Model} & \textbf{Top-1} & \textbf{mIoU} & \textbf{RMSE} $\downarrow$ \\
        \midrule
        DeiT-III ViT-B/16            & \textbf{96.67} & 12.89 & 3.059 m \\
        DeiT-III +reg4 (injected)    & 96.00 & \textbf{13.27} & \textbf{3.036 m} \\
        \midrule
        OpenCLIP ViT-B/16            & 90.67 & 12.16 & 1.746 m \\
        OpenCLIP +tt-reg4 (Jiang)    & 90.67 & \textbf{12.36} & \textbf{1.550 m} \\
        \midrule
        DINOv2 ViT-L/14              & 94.00 & 18.70 & 1.974 m \\
        DINOv2 ViT-L/14 +reg4        & \textbf{94.67} & \textbf{19.19} & \textbf{1.199 m} \\
        \bottomrule
        \end{tabular}
        &
        \begin{tabular}[b]{lc}
        \toprule
        & \textbf{ImageNet} \\
        \textbf{Model} & \textbf{Top-1} \\
        \midrule
        OpenCLIP ViT-B/16         & \textbf{94.00} \\
        OpenCLIP +tt-reg4 (Jiang) & 93.33 \\
        \bottomrule
        \end{tabular}
        \\[2pt]
        \footnotesize (a) Linear evaluation with frozen features.
        &
        \footnotesize (b) Zero-shot classification.
    \end{tabular}}
    \par\vspace{4pt}
    \captionsetup{position=below}
    \captionof{table}{Reproduction of Table~2 from \citet{darcet2024vision}: (a) linear probes on frozen features; (b) OpenCLIP zero-shot Top-1 with the 11-prompt ensemble. Model checkpoints in Table~\ref{tab:models}, dataset details in Table~\ref{tab:datasets}.}
    \label{tab:t2ab}
\end{minipage}

\vspace{4pt}
The DINOv2 row is the cleanest comparison (both checkpoints from the original paper) and reproduces the central claim: trained registers improve all three probes ($+0.67$~pt Top-1, $+0.49$~pt mIoU, $-0.775$~m RMSE, i.e.\ a $39\%$ relative reduction). OpenCLIP with test-time registers shows no Top-1 change and small dense-prediction gains, consistent with \citet{jiang2025vision}; the $-0.67$~pt zero-shot drop (one misclassified image on 150) is within subset variance. DeiT-III with injected \emph{untrained} register-token parameters regresses $-0.67$~pt on Top-1 but still improves mIoU and RMSE, suggesting that even random register slots act as a partial sink for high-norm outliers -- evidence in favour of the paper's mechanistic interpretation that registers' role is to absorb artifact tokens rather than to carry trained information.

\subsubsubsection{Figure 8 -- Attention maps and linear evaluation vs.\ number of registers}

\citet{darcet2024vision} sweep $N\in\{0,1,2,4,8,16\}$ register tokens by retraining DINOv2 from scratch for each value -- a regime out of our compute budget. We instead compare three retraining-free approximations defined in Section~\ref{sec:method-P}. Qualitative attention maps for all three are stacked in Figure~\ref{fig:f8-top} (appendix); the corresponding downstream metrics are in Figure~\ref{fig:f8-bot} and Table~\ref{tab:f8} (appendix). Numerical values for the truncate/cycle proxy are: $N=0\!\to\!70.67\%$ Top-1 (collapse, model expects 4 registers); $N=1\!\to\!93.33\%$; $N=2\!\to\!92.67\%$; $N=4\!\to\!94.67\%$; $N=8\!\to\!94.67\%$; $N=16\!\to\!95.33\%$. For the Jiang and independent variants on the unmodified DINOv2 baseline, Top-1 jumps from $94.00\%$ at $N=0$ to $95.33\%$ at $N=1$ and remains flat through $N=8$, before collapsing sharply at $N=16$ ($92.00\%$ for Jiang, $92.67\%$ for the independent variant). Both methods qualitatively reproduce the paper's key finding -- a single register is sufficient to absorb the high-norm outlier and stabilise the attention map -- and the magnitudes of the $N=0\!\to\!1$ jump are consistent in sign with the paper, although our absolute values lie above the paper's because our 50-class ImageNet subset is much easier than the full 1000-class benchmark.

\subsubsection{Results beyond original paper}

\subsubsubsection{Independent variant of the Jiang test-time register intervention}

A close reading of Jiang's code (\texttt{shared/hook\_fn.py}, function \texttt{activate\_on\_registers}) reveals that for each register neuron the top-1 outlier value is duplicated identically across all $N$ test-time registers. The collapse we observe at $N=16$ might therefore be caused by the CLS token attending to 16 near-identical broadcast nodes and diluting its global readout. To test this we introduced a controlled variant in which, for each neuron, the top-$N$ distinct outlier patches are picked and their signed values are written onto $N$ different registers (so register $i$ receives the $(i{+}1)$-th outlier). Patch positions are zeroed exactly as in Jiang's pipeline. The numerical results are reported alongside the Jiang re-implementation in Table~\ref{tab:f8} (appendix); the qualitative attention maps are in Figure~\ref{fig:f8-top} row~3. \textbf{The hypothesis is falsified}: the $N=16$ collapse persists ($92.67\%$ vs.\ $92.00\%$ for Jiang), the Top-1 profile is otherwise identical to Jiang's, and diagnostic measurements confirm that the patch-token norms after the intervention are clean at all $N\geq 1$ (max patch norm $\sim 51$, no patch above $60$). Since neither the writing policy nor residual artifacts on the patches explain the collapse, the failure mode must lie in the downstream transformer blocks (18--23 of DINOv2 ViT-L/14) that follow the intervention point and were never trained to process so many simultaneously active broadcast tokens. This is a falsifiable finding that does not appear in either source paper.
